---
title: "SocKultExam"
author: "Lasse Hansen"
date: "May 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
setwd("~/Desktop/SocKultExam/Audio_Speech_Actors_01-24")

p_load(tidyverse, rethinking, brms, glmnet, lme4, caret, groupdata2, pROC)
```
    Modality (01 = full-AV, 02 = video-only, 03 = audio-only).
    Vocal channel (01 = speech, 02 = song).
    Emotion (01 = neutral, 02 = calm, 03 = happy, 04 = sad, 05 = angry, 06 = fearful, 07 = disgust, 08 = surprised).
    Emotional intensity (01 = normal, 02 = strong). NOTE: There is no strong intensity for the 'neutral' emotion.
    Statement (01 = "Kids are talking by the door", 02 = "Dogs are sitting by the door").
    Repetition (01 = 1st repetition, 02 = 2nd repetition).
    Actor (01 to 24. Odd numbered actors are male, even numbered actors are female).

##Function to load, add column for filename, and trim the dfs so only rows where there is speech are kept
```{r}
trimload = function(file){
  df = read_csv(file)
  df = df[!df$NAQ==0,]
  df$filename = as.factor(file)
  return(df)
}
```


#Preprocessing. Loading and adding identification columns
```{r}
#creating a list of the folders where the files are
folders = list.files(pattern = "Actor*")
#creating a list of all the .csv files in all the folders
file.list <- list.files(folders, pattern = '*.csv', full.names = T)


#reading all the csv files in the file.list
df.list <- lapply(file.list, trimload)
#turning into a data frame
dfTrim = bind_rows(df.list)

#adding identification columns
dfTrim$emotion = as.numeric(str_sub(dfTrim$filename, start = 16, end = 17))
dfTrim$intensity = as.numeric(str_sub(dfTrim$filename, start = 19, end = 20))
dfTrim$statement = as.numeric(str_sub(dfTrim$filename, start = 22, end = 23))
dfTrim$repetition = as.numeric(str_sub(dfTrim$filename, start = 25, end = 26))
dfTrim$actor = as.numeric(str_sub(dfTrim$filename, start = 28, end = 29))
#adding gender column
dfTrim$gender = as.factor(ifelse(dfTrim$actor %% 2 == 0, 'female', 'male'))
#adding dummy columns for each emotion we are interested in   
dfTrim$neutral = ifelse(dfTrim$emotion == 1, 1, 0)
dfTrim$happy = ifelse(dfTrim$emotion == 3, 1, 0)
dfTrim$sad = ifelse(dfTrim$emotion == 4, 1, 0)
dfTrim$angry = ifelse(dfTrim$emotion == 5, 1, 0)

#creating subset of data containing only the emotions we are interested in
dfTrim2 = dfTrim %>% filter(neutral == 1 | happy == 1 | sad == 1 | angry == 1)

#saving files
#write.csv(dfTrim, file = "allDataTrim.csv")
#write.csv(dfTrim2, file = "filteredEmotionsTrim.csv")
```

#Summarising with median and IQR
```{r}
df = read_csv("filteredEmotionsTrim.csv")
df$X1 = NULL

df = df[complete.cases(df),]


sumdf = df %>% 
  group_by(filename) %>% 
  summarise_at(.vars = names(.)[1:81],
               .funs = c(median="median", IQR = "IQR"))
#adding IDs
df$emotion = as.numeric(str_sub(df$filename, start = 16, end = 17))
df$intensity = as.numeric(str_sub(df$filename, start = 19, end = 20))
df$statement = as.numeric(str_sub(df$filename, start = 22, end = 23))
df$repetition = as.numeric(str_sub(df$filename, start = 25, end = 26))
df$actor = as.numeric(str_sub(df$filename, start = 28, end = 29))
#adding gender column
df$gender = as.factor(ifelse(df$actor %% 2 == 0, 'female', 'male'))
#adding dummy columns for each emotion we are interested in   
df$neutral = ifelse(df$emotion == 1, 1, 0)
df$happy = ifelse(df$emotion == 3, 1, 0)
df$sad = ifelse(df$emotion == 4, 1, 0)
df$angry = ifelse(df$emotion == 5, 1, 0)

#write.csv(df, file = "TrimSumData.csv")

```


#Preparing data for elastic net
```{r}
df <- read.csv("TrimSumData.csv")
df$X <- NULL

#removing columns with only zeros (become NA's when scaled = glmnet not happy)
df$HMPDM_0_median <- NULL
df$HMPDM_0_IQR <- NULL
df$HMPDM_1_median <- NULL
df$HMPDM_1_IQR <- NULL
df$vowelSpace_median <- NULL
df$vowelSpace_IQR <- NULL

#only keeping neutral, happy, sad, angry
df = df %>% filter(emotion == 3 | emotion == 5 | emotion == 1 | emotion == 4)


#creating predictor column 
Predictors <- df[, -c(158:168)]
Predictors$filename = NULL

#Creating outcome variables
yAngry <- select(df, angry)
ySad <- select(df, sad)
yNeutral <- select(df, neutral)
yHappy <- select(df, happy)

#no NA's 
#identical(Predictors, Predictors[complete.cases(Predictors),])
```

##Running the elastic net
```{r}
## Define predictors and outcome
x   <- model.matrix(~.-1, data= Predictors) # where all the columns except the first are predictors

# makes outcome variables into a non data frame because glmnet doesn’t deal with dataframes
yAngry=as.numeric(unlist(yAngry))
ySad=as.numeric(unlist(ySad))
yNeutral=as.numeric(unlist(yNeutral))
yHappy=as.numeric(unlist(yHappy))


#scale all features
x=scale(x)[,] ##testing

#function to run the elastic net. First chooses the optimal alpha, then runs the elastic net
elasticfun = function(y){
  # Define cross-validated alpha selection (alpha indicates how strong the correlation btw predictors should be for it to be taken   into account when discarding predictors)
  alphaslist<-seq(0,1,by=0.1)
  foldslist<-seq(4,12)
  pars=expand.grid(alphaslist,foldslist)

  cvm1=matrix(rep(0,length(alphaslist)))

  elasticnet1<-lapply(1:length(cvm1), 
                  function(a){
                    cv.glmnet(x, y, alpha=alphaslist[a], family="binomial", 
                                                         lambda.min.ratio=.001,nfolds = 5)})

  for (i in 1:length(alphaslist)) {cvm1[i]=min(elasticnet1[[i]]$cvm)}

  n1=which(cvm1==min(cvm1))

  alpha1=alphaslist[n1]

# Run cross-validated elastic net with the chosen alpha (to choose lambda)
  mod_cv <- cv.glmnet(x=x, y=y, family='binomial', alpha=alpha1, nfolds=5) # Modify family if not binomial
  coefs=as.data.frame(as.matrix(coef(mod_cv, mod_cv$lambda.1se)))
  coefs$predictors<-rownames(coefs)
  rownames(coefs) <- NULL
  names(coefs)[1] <- "betas"
  coefs=subset(coefs,betas!=0)
  coefs1=coefs[order(abs(coefs$betas)),]
  return(coefs1)
}


angryNet = elasticfun(yAngry)
sadNet = elasticfun(ySad)
neutralNet = elasticfun(yNeutral)
happyNet = elasticfun(yHappy)

# #saving values
# save(angryNet, file = "angryNet.RData")
# save(sadNet, file = "sadNet.RData")
# save(neutralNet, file = "neutralNet.RData")
# save(happyNet, file = "happyNet.RData")

load('angryNet.RData')
load('sadNet.RData')
load('neutralNet.RData')
load('happyNet.RData')
```

##Creating models and calculating confusion matrix
```{r}
#scaling all variables
df[,2:157] = as.data.frame(apply(df[,2:157],2,scale))

#model predicting happy, using the features with a beta > .1 og < -.1 in the elastic net
happyFitFull <- brm(happy ~ MCEP_20_IQR + MCEP_5_median + HMPDD_11_IQR + MCEP_8_IQR + MCEP_23_median + HMPDD_2_IQR + f0_IQR + MCEP_3_median + MCEP_8_median + MCEP_2_IQR + MCEP_1_median + MCEP_11_median + HMPDD_0_median + MCEP_11_IQR + MCEP_4_median + MCEP_6_median +  (1|actor) + (1|intensity), 
            data = df, family = bernoulli(), cores = 4, chains = 4, control = list( adapt_delta = .99))

#model predicting sad, using the features with a beta > .1 og < -.1 in the elastic net
sadFitFull <- brm(sad ~  MCEP_23_IQR + MCEP_13_IQR + F4_IQR + MCEP_16_IQR + MCEP_12_median + HMPDM_3_median + F2_median + MCEP_15_IQR +  MCEP_6_IQR + HMPDD_11_median + MDQ_median + MCEP_3_IQR + MCEP_7_median + NAQ_IQR + MCEP_18_IQR + MCEP_0_IQR + MCEP_0_median + f0_IQR + (1|actor) + (1|intensity), 
            data = df, family = bernoulli(), cores = 4, chains = 4, control = list( adapt_delta = .99))

#model predicting angry, using the features with a beta > .1 og < -.1 in the elastic net
angryFitFull <- brm(angry ~ HMPDD_9_median + PSP_median + PSP_median + HMPDD_1_median + Rd_conf_IQR + MCEP_4_median + MCEP_24_IQR + MCEP_6_IQR +  HMPDD_6_IQR + MCEP_18_median + peakSlope_median + MCEP_3_IQR + MCEP_13_median + MCEP_2_IQR + MCEP_24_median + MCEP_6_median + Rd_conf_median + MCEP_11_median + MCEP_15_median + MCEP_2_median + MCEP_7_median + MCEP_8_median + MCEP_0_IQR + MCEP_0_median + MCEP_7_IQR + (1|actor) + (1|intensity),
                data = df, family = bernoulli(), cores = 4, chains = 4, control = list(adapt_delta = .99))

#model predicting neutral, using the features with a beta > .1 og < -.1 in the elastic net
neutralFitFull <- brm(neutral ~  MCEP_24_median + MCEP_13_median + HMPDM_3_IQR + NAQ_IQR + QOQ_median +  MCEP_2_median + MCEP_0_median + MCEP_19_median + NAQ_median + VUV_IQR + (1|actor) + (1|intensity), 
            data = df, family = bernoulli(), cores = 4, chains = 4, control = list( adapt_delta = .99))

save(happyFitFull, file = 'happyFitFull.RData')
save(angryFitFull, file= 'angryFitFull.RData')
save(sadFitFull, file = 'sadFitFull.RData')
save(neutralFitFull, file = 'neutralFitFull.RData')


load('happyFitFull1.RData')
load('sadFitFull1.RData')
load('angryFitFull1.RData')
load('neutralFitFull1.RData')

preddf = df

#calculating predictions
#adding [,1] to only get the estimate (don't care about uncertainty right now)
preddf$predAngry = predict(angryFitFull, preddf, re_formula = NA)[,1]
preddf$predHappy = predict(happyFitFull, preddf, re_formula = NA)[,1]
preddf$predSad = predict(sadFitFull, preddf, re_formula = NA)[,1]
preddf$predNeutral = predict(neutralFitFull, preddf, re_formula = NA)[,1]



#Recoding the factor levels for interpretability
preddf$emotion = as.factor(recode(preddf$emotion, '3' = 'Happy', '5' = 'Angry', '1' = 'Neutral', '4' = 'Sad'))
#Adding a column which selects the most confident prediction from the 4 models
preddf = preddf %>%
  select(predAngry, predHappy, predSad, predNeutral, emotion) %>%
  mutate(
    predictions = case_when(
      predAngry > predHappy & predAngry > predSad & predAngry > predNeutral ~ "Angry",
      predHappy > predAngry & predHappy > predSad & predHappy > predNeutral ~ "Happy",
      predSad > predAngry & predSad > predHappy & predSad > predNeutral ~ 'Sad',
      TRUE                      ~  "Neutral" ))

preddf$predictions = as.factor(preddf$predictions)
#calculating confusion matrix
conf = confusionMatrix(data = preddf$predictions, reference = preddf$emotion)
conf

```

#Calculating AUCs and creating ROC curves for each emotions vs all the others
```{r}
##angry roc
angrydf = preddf
angrydf$emotion = as.factor(recode(angrydf$emotion, 'Happy' = '0', 'Angry' = '1', 'Neutral' = '0', 'Sad' = '0'))
angrydf$predictions = as.factor(recode(angrydf$predictions, 'Happy' = '0', 'Angry' = '1', 'Neutral' = '0', 'Sad' = '0'))

angrydf$emotion = relevel(angrydf$emotion, ref = "0")
angrydf$predictions = relevel(angrydf$predictions, ref = "0")

angrydf$predictions = as.numeric(angrydf$predictions)

AngryrocCurve = roc(response = angrydf$emotion, predictor = angrydf$predictions)
Angryauc = auc(AngryrocCurve)
Angryaucci = ci(AngryrocCurve)


##happy roc
happydf = preddf
happydf$emotion = as.factor(recode(happydf$emotion, 'Happy' = '1', 'Angry' = '0', 'Neutral' = '0', 'Sad' = '0'))
happydf$predictions = as.factor(recode(happydf$predictions, 'Happy' = '1', 'Angry' = '0', 'Neutral' = '0', 'Sad' = '0'))

happydf$emotion = relevel(happydf$emotion, ref = "0")
happydf$predictions = relevel(happydf$predictions, ref = "0")

happydf$predictions = as.numeric(happydf$predictions)

HappyrocCurve = roc(response = happydf$emotion, predictor = happydf$predictions)
Happyauc = auc(HappyrocCurve)
Happyaucci = ci(HappyrocCurve)

##sad roc
saddf = preddf
saddf$emotion = as.factor(recode(saddf$emotion, 'Happy' = '0', 'Angry' = '0', 'Neutral' = '0', 'Sad' = '1'))
saddf$predictions = as.factor(recode(saddf$predictions, 'Happy' = '0', 'Angry' = '0', 'Neutral' = '0', 'Sad' = '1'))

saddf$emotion = relevel(saddf$emotion, ref = "0")
saddf$predictions = relevel(saddf$predictions, ref = "0")

saddf$predictions = as.numeric(saddf$predictions)

SadrocCurve = roc(response = saddf$emotion, predictor = saddf$predictions)
Sadauc = auc(SadrocCurve)
Sadaucci = ci(SadrocCurve)


##neutral roc
neutraldf = preddf
neutraldf$emotion = as.factor(recode(neutraldf$emotion, 'Happy' = '0', 'Angry' = '0', 'Neutral' = '1', 'Sad' = '0'))
neutraldf$predictions = as.factor(recode(neutraldf$predictions, 'Happy' = '0', 'Angry' = '0', 'Neutral' = '1', 'Sad' = '0'))

neutraldf$emotion = relevel(neutraldf$emotion, ref = "0")
neutraldf$predictions = relevel(neutraldf$predictions, ref = "0")

neutraldf$predictions = as.numeric(neutraldf$predictions)

NeutralrocCurve = roc(response = neutraldf$emotion, predictor = neutraldf$predictions)
Neutralauc = auc(NeutralrocCurve)
Neutralaucci = ci(NeutralrocCurve)



AUCs = c(Angryauc,Happyauc, Neutralauc,Sadauc)
AUCs

Angryaucci
Happyaucci
Neutralaucci
Sadaucci

#ROC curves
par(pty="s")
plot(AngryrocCurve, legacy.axes = T, col = 'red')
plot(HappyrocCurve, legacy.axes = T, add = T, col ='green')
plot(SadrocCurve, legacy.axes = T, add = T, col = 'blue')
plot(NeutralrocCurve, legacy.axes = T, add = T)
legend("bottomright", inset = 0.02, legend = c("Angry", "Sad", "Happy", "Neutral"), col = c("red", "blue", "green", "black"), lty = 1, cex = 0.8)
title("ROC for each emotion vs all others", cex = 0.8, line = 2.5)

#Multiclass ROC
preddf$predictions = as.ordered(preddf$predictions)
multiClass = multiclass.roc(response = preddf$emotion, predictor = preddf$prediction)
multiClass
```

#4-fold Cross-validation
```{r}
#setting number of folds
nfolds = 4
#adding folds, splitting evenly by emotion
df = fold(df, k = nfolds, cat_col = 'emotion')
df = as.data.frame(df)

#running cross-validation loop (beware, takes ~20 hours)
for (i in 1:4){
  train = df[df$.folds != i,]    #creating training set (all folds except the one)
  validation = df[df$.folds == i,] #creating testing/validation set (the current fold)
  
  happyModel =  brm(happy ~ MCEP_20_IQR + MCEP_5_median + HMPDD_11_IQR + MCEP_8_IQR + MCEP_23_median + HMPDD_2_IQR + f0_IQR + MCEP_3_median + MCEP_8_median + MCEP_2_IQR + MCEP_1_median + MCEP_11_median + HMPDD_0_median + MCEP_11_IQR + MCEP_4_median + MCEP_6_median +  (1|actor) + (1|intensity), 
            data =train, family = bernoulli(), cores = 4, chains = 4, control = list( adapt_delta = .99))  
  
  angryModel = brm(angry ~ HMPDD_9_median + PSP_median + PSP_median + HMPDD_1_median + Rd_conf_IQR + MCEP_4_median + MCEP_24_IQR + MCEP_6_IQR +  HMPDD_6_IQR + MCEP_18_median + peakSlope_median + MCEP_3_IQR + MCEP_13_median + MCEP_2_IQR + MCEP_24_median + MCEP_6_median + Rd_conf_median + MCEP_11_median + MCEP_15_median + MCEP_2_median + MCEP_7_median + MCEP_8_median + MCEP_0_IQR + MCEP_0_median + MCEP_7_IQR + (1|actor) + (1|intensity),
                data = train, family = bernoulli(), cores = 4, chains = 4, control = list(adapt_delta = .99))
  
  sadModel = brm(sad ~  MCEP_23_IQR + MCEP_13_IQR + F4_IQR + MCEP_16_IQR + MCEP_12_median + HMPDM_3_median + F2_median + MCEP_15_IQR +  MCEP_6_IQR + HMPDD_11_median + MDQ_median + MCEP_3_IQR + MCEP_7_median + NAQ_IQR + MCEP_18_IQR + MCEP_0_IQR + MCEP_0_median + f0_IQR + (1|actor) + (1|intensity), 
            data = train, family = bernoulli(), cores = 4, chains = 4, control = list( adapt_delta = .99))
  
  neutralModel = brm(neutral ~  MCEP_24_median + MCEP_13_median + HMPDM_3_IQR + NAQ_IQR + QOQ_median +  MCEP_2_median + MCEP_0_median + MCEP_19_median + NAQ_median + VUV_IQR + (1|actor) + (1|intensity) , 
            data = train, family = bernoulli(), cores = 4, chains = 4, control = list( adapt_delta = .99))
  #adding predictions  
  validation$predAngry = NA
  validation$predHappy = NA
  validation$predSad = NA
  validation$predNeutral = NA
  
  validation$predAngry = predict(angryModel, validation, re_formula = NA)[,1]
  validation$predHappy = predict(happyModel, validation, re_formula = NA)[,1]
  validation$predSad = predict(sadModel, validation, re_formula = NA)[,1]
  validation$predNeutral = predict(neutralModel, validation, re_formula = NA)[,1]  
  #removes column (sometimes necessary to avoid errors)
  validation$predictions = NA
  
  validation$emotion = as.factor(recode(validation$emotion, '3' = 'Happy', '5' = 'Angry', '1' = 'Neutral', '4' = 'Sad'))
  
  validation = validation %>%
  select(predAngry, predHappy, predSad, predNeutral, emotion) %>%
  mutate(
    predictions = case_when(
      predAngry > predHappy & predAngry > predSad & predAngry > predNeutral ~ "Angry",
      predHappy > predAngry & predHappy > predSad & predHappy > predNeutral ~ "Happy",
      predSad > predAngry & predSad > predHappy & predSad > predNeutral ~ 'Sad',
      TRUE                      ~  "Neutral" ))

  validation$predictions = as.factor(validation$predictions)
  #confusionmatrix ####################################################################
  conf = confusionMatrix(data = validation$predictions, reference = validation$emotion)
  #individual ROCS###################################################################
  
  ##angry roc
  angrydf = validation
  angrydf$emotion = as.factor(recode(angrydf$emotion, 'Happy' = '0', 'Angry' = '1', 'Neutral' = '0', 'Sad' = '0'))
  angrydf$predictions = as.factor(recode(angrydf$predictions, 'Happy' = '0', 'Angry' = '1', 'Neutral' = '0', 'Sad' = '0'))

  angrydf$emotion = relevel(angrydf$emotion, ref = "0")
  angrydf$predictions = relevel(angrydf$predictions, ref = "0")

  angrydf$predictions = as.numeric(angrydf$predictions)

  angryRoc = roc(response = angrydf$emotion, predictor = angrydf$predictions)
  angryAuc = auc(angryRoc)
  angryAucci = ci(angryRoc)

  ##happy roc
  happydf = validation
  happydf$emotion = as.factor(recode(happydf$emotion, 'Happy' = '1', 'Angry' = '0', 'Neutral' = '0', 'Sad' = '0'))
  happydf$predictions = as.factor(recode(happydf$predictions, 'Happy' = '1', 'Angry' = '0', 'Neutral' = '0', 'Sad' = '0'))

  happydf$emotion = relevel(happydf$emotion, ref = "0")
  happydf$predictions = relevel(happydf$predictions, ref = "0")

  happydf$predictions = as.numeric(happydf$predictions)

  happyRoc= roc(response = happydf$emotion, predictor = happydf$predictions)
  happyAuc = auc(happyRoc)
  happyAucci = ci(happyRoc)

  ##sad roc
  saddf = validation
  saddf$emotion = as.factor(recode(saddf$emotion, 'Happy' = '0', 'Angry' = '0', 'Neutral' = '0', 'Sad' = '1'))
  saddf$predictions = as.factor(recode(saddf$predictions, 'Happy' = '0', 'Angry' = '0', 'Neutral' = '0', 'Sad' = '1'))

  saddf$emotion = relevel(saddf$emotion, ref = "0")
  saddf$predictions = relevel(saddf$predictions, ref = "0")

  saddf$predictions = as.numeric(saddf$predictions)

  sadRoc = roc(response = saddf$emotion, predictor = saddf$predictions)
  sadAuc = auc(sadRoc)
  sadAucci = ci(sadRoc)

  ##neutral roc
  neutraldf = validation
  neutraldf$emotion = as.factor(recode(neutraldf$emotion, 'Happy' = '0', 'Angry' = '0', 'Neutral' = '1', 'Sad' = '0'))
  neutraldf$predictions = as.factor(recode(neutraldf$predictions, 'Happy' = '0', 'Angry' = '0', 'Neutral' = '1', 'Sad' = '0'))

  neutraldf$emotion = relevel(neutraldf$emotion, ref = "0")
  neutraldf$predictions = relevel(neutraldf$predictions, ref = "0")

  neutraldf$predictions = as.numeric(neutraldf$predictions)

  neutralRoc = roc(response = neutraldf$emotion, predictor = neutraldf$predictions)
  neutralAuc = auc(neutralRoc)
  neutralAucci = ci(neutralRoc)
  
  ##MULTICLASS
  validation$predictions = as.ordered(validation$predictions)
  multiClass = multiclass.roc(response = validation$emotion, predictor = validation$prediction)
  
  
  #adding results to df
  results = data.frame(Accuracy = conf$overall[1],
                       Kappa = conf$overall[2],
                       ConfLower = conf$overall[3],
                       ConfUpper = conf$overall[4],
                       
                       AngrySensitivity = conf$byClass[1],
                       Happyensitivity = conf$byClass[2],
                       NeutralSensitivity = conf$byClass[3],
                       SadSensitivity = conf$byClass[4],
                       
                       AngrySpecificity = conf$byClass[5],
                       HappySpecificity = conf$byClass[6],
                       NeutralSpecificity = conf$byClass[7],
                       SadSpecificity = conf$byClass[8],
                       
                       AngryPPV = conf$byClass[9],
                       HappyPPV = conf$byClass[10],
                       NeutralPPV = conf$byClass[11],
                       SadPPV = conf$byClass[12],
                       
                       AngryNPV = conf$byClass[13],
                       HappyNPV = conf$byClass[14],
                       NeutralNPV = conf$byClass[15],
                       SadNPV = conf$byClass[16],
                       
                       AngryPrecision = conf$byClass[17],
                       HappyPrecision = conf$byClass[18],
                       NeutralPrecision = conf$byClass[19],
                       SadPrecision = conf$byClass[20],
                       
                       AngryRecall = conf$byClass[21],
                       HappyRecall = conf$byClass[22],
                       NeutralRecall = conf$byClass[23],
                       SadRecall = conf$byClass[24],
                       
                       AngryF1 = conf$byClass[25],
                       HappyF1 = conf$byClass[26],
                       NeutralF1 = conf$byClass[27],
                       SadF1 = conf$byClass[28],
                       
                       AngryDetectionRate = conf$byClass[33],
                       HappyDetectionRate = conf$byClass[34],
                       NeutralDetectionRate = conf$byClass[35],
                       SadDetectionRate = conf$byClass[36],
                       
                       AngryDetectionPrevalence = conf$byClass[37],
                       HappyDetectionPrevalence = conf$byClass[38],
                       NeutralDetectionPrevalence = conf$byClass[39],
                       SadDetectionPrevalence = conf$byClass[40],
                       
                       AngryBalancedAccuracy = conf$byClass[41],
                       HappyBalancedAccuracy = conf$byClass[42],
                       NeutralBalancedAccuracy = conf$byClass[43],
                       SadBalancedAccuracy = conf$byClass[44],
                       
                       AngryAUC = angryAuc[1],
                       HappyAUC = happyAuc[1],
                       NeutralAUC = neutralAuc[1],
                       SadAUC = sadAuc[1],
                       
                       AngryAUCLower = angryAucci[1],
                       HappyAUCLower = happyAucci[1],
                       NeutralAUCLower = neutralAucci[1],
                       SadAUCLower = sadAucci[1],
                       
                       AngryAUCUpper = angryAucci[3],
                       HappyAUCUpper = happyAucci[3],
                       NeutralAUCUpper = neutralAucci[3],
                       SadAUCUpper = sadAucci[3],
                    
                       row.names = NULL)
  if(i == 1){
    result_df = results
  }else{
    result_df = rbind(result_df, results)
  }
  
}

save(result_df, file = 'cv_results.RData')



```

#Summarizing results
```{r}
sum_results = result_df %>% 
  summarise_at(.vars = names(.)[1:56],
               .funs = c(mean="mean"))

```

#Testing on other datasets
#UMSSED dataset
#Loading and merging data
```{r}
setwd("~/Desktop/SocKultExam/mp3")

#creating a list of the folders where the files are
folders = list.files(path = "/home/lasse/Desktop/SocKultExam/mp3")
#creating a list of all the .csv files in all the folders
file.list <- list.files(folders, pattern = '*.csv', full.names = T)
folders = folders[2]
#reading all the csv files in the file.list
df.list <- lapply(file.list, trimload)
#turning into a data frame
dfTrim = bind_rows(df.list)

dfTrim = as.data.frame(dfTrim)

```

#Summarizing testing data
```{r}
df = dfTrim

df = df[complete.cases(df),]


sumdf = df %>% 
  group_by(filename) %>% 
  summarise_at(.vars = names(.)[1:81],
               .funs = c(median="median", IQR = "IQR"))

sumdf = as.data.frame(sumdf)

#adding IDs
sumdf$emotion = str_sub(sumdf$filename, start = 16, end = 16)
sumdf$actor = str_sub(sumdf$filename, start = 1, end = 2)

#adding dummy columns for each emotion we are interested in   
sumdf$neutral = ifelse(sumdf$emotion == "N", 1, 0)
sumdf$happy = ifelse(sumdf$emotion == "H", 1, 0)
sumdf$sad = ifelse(sumdf$emotion == "S", 1, 0)
sumdf$angry = ifelse(sumdf$emotion == "A", 1, 0)

write.csv(sumdf, file = "UMSSEDTrimSumData.csv")
```

#Testing predictions
```{r}
setwd("~/Desktop/SocKultExam/mp3")

preddf = read.csv("UMSSEDTrimSumData.csv")
preddf$X = NULL

setwd("~/Desktop/SocKultExam/Audio_Speech_Actors_01-24")

load('happyFitFull1.RData')
load('sadFitFull1.RData')
load('angryFitFull1.RData')
load('neutralFitFull1.RData')


#adding [,1] to only get the estimate (don't care about uncertainty right now)
preddf$predAngry = predict(angryFitFull, preddf, re_formula = NA)[,1]
preddf$predHappy = predict(happyFitFull, preddf, re_formula = NA)[,1]
preddf$predSad = predict(sadFitFull, preddf, re_formula = NA)[,1]
preddf$predNeutral = predict(neutralFitFull, preddf, re_formula = NA)[,1]


preddf$emotion = as.factor(recode(preddf$emotion, 'H' = 'Happy', 'A' = 'Angry', 'N' = 'Neutral', 'S' = 'Sad'))

preddf = preddf %>%
  select(predAngry, predHappy, predSad, predNeutral, emotion) %>%
  mutate(
    predictions = case_when(
      predAngry > predHappy & predAngry > predSad & predAngry > predNeutral ~ "Angry",
      predHappy > predAngry & predHappy > predSad & predHappy > predNeutral ~ "Happy",
      predSad > predAngry & predSad > predHappy & predSad > predNeutral ~ 'Sad',
      TRUE                      ~  "Neutral" ))

preddf$predictions = as.factor(preddf$predictions)

conf = confusionMatrix(data = preddf$predictions, reference = preddf$emotion)
conf
#Everything's happy :( :( :(

preddf$predictions = as.ordered(preddf$predictions)
multiClass = multiclass.roc(response = preddf$emotion, predictor = preddf$prediction)
multiClass
```
##Practically everything is predicted as happy. Angry predicts close to zero everytime.

#Testing prediction on the SAVEE dataset
#Loading and merging data
```{r}
setwd("~/Desktop/SocKultExam/AudioData")

#creating a list of the folders where the files are
folders = list.files(path = "/home/lasse/Desktop/SocKultExam/AudioData")
#creating a list of all the .csv files in all the folders
file.list <- list.files(folders, pattern = '*.csv', full.names = T)
#reading all the csv files in the file.list
df.list <- lapply(file.list, trimload)
#turning into a data frame
dfTrim = bind_rows(df.list)

dfTrim = as.data.frame(dfTrim)

```

#Summarizing testing data
```{r}
df = dfTrim

df = df[complete.cases(df),]


sumdf = df %>% 
  group_by(filename) %>% 
  summarise_at(.vars = names(.)[1:81],
               .funs = c(median="median", IQR = "IQR"))

sumdf = as.data.frame(sumdf)

#adding IDs
sumdf$emotion = str_sub(sumdf$filename, start = 4, end = 4)
sumdf$actor = str_sub(sumdf$filename, start = 1, end = 2)

#adding dummy columns for each emotion we are interested in   
sumdf$neutral = ifelse(sumdf$emotion == "n", 1, 0)
sumdf$happy = ifelse(sumdf$emotion == "h", 1, 0)
sumdf$sad = ifelse(sumdf$emotion == "s", 1, 0)
sumdf$angry = ifelse(sumdf$emotion == "a", 1, 0)

write.csv(sumdf, file = "SAVEETrimSumData.csv")
```

#Testing predictions
```{r}
setwd("~/Desktop/SocKultExam/AudioData")

preddf = read.csv("SAVEETrimSumData.csv")
preddf$X = NULL

setwd("~/Desktop/SocKultExam/Audio_Speech_Actors_01-24")

load('happyFitFull1.RData')
load('sadFitFull1.RData')
load('angryFitFull1.RData')
load('neutralFitFull1.RData')


#adding [,1] to only get the estimate (don't care about uncertainty right now)
preddf$predAngry = predict(angryFitFull, preddf, re_formula = NA)[,1]
preddf$predHappy = predict(happyFitFull, preddf, re_formula = NA)[,1]
preddf$predSad = predict(sadFitFull, preddf, re_formula = NA)[,1]
preddf$predNeutral = predict(neutralFitFull, preddf, re_formula = NA)[,1]


preddf$emotion = as.factor(recode(preddf$emotion, 'h' = 'Happy', 'a' = 'Angry', 'n' = 'Neutral', 's' = 'Sad'))

preddf = preddf %>%
  select(predAngry, predHappy, predSad, predNeutral, emotion) %>%
  mutate(
    predictions = case_when(
      predAngry > predHappy & predAngry > predSad & predAngry > predNeutral ~ "Angry",
      predHappy > predAngry & predHappy > predSad & predHappy > predNeutral ~ "Happy",
      predSad > predAngry & predSad > predHappy & predSad > predNeutral ~ 'Sad',
      TRUE                      ~  "Neutral" ))

preddf$predictions = as.factor(preddf$predictions)

conf = confusionMatrix(data = preddf$predictions, reference = preddf$emotion)
conf
#Everything's happy :( :( :(

preddf$predictions = as.ordered(preddf$predictions)
multiClass = multiclass.roc(response = preddf$emotion, predictor = preddf$prediction)
multiClass
```
##EVERYTHING is predicted as happy. Angry predicts close to zero everytime.




